### 2018-03-26 Sections/quality_of_service.tex
Torus pic

Importantly, topological codes do not require joint measurements across the entire graph state, instead requiring only operations localised to small regions within the graph. Thanks to this, computation using such topological codes can remain distributed, without requiring the entire state to be held locally by a particular host, or requiring full access to the entire state by any particular user.

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{torus_paulis}
	\caption{Implementation of logical Pauli-$\hat{X}$ (\comment{which colour?}) and -$\hat{Z}$ (\comment{which colour?}) operations on a toric code qubit via the application of a chain of local Paulis. The chains must circumvent the torus around either axis. Any path topologically equivalent to such a circumvention of the torus is sufficient, enabling paths to bypass defects in the lattice.} \label{fig:toric_code_paulis}
\end{figure}

@@

%
%
% Topological Codes
%

\subsection{Topological codes} \label{sec:topol_codes} \index{Topological codes}

\comment{Toric code -- shift this to surface code section}

Currently, topological codes (Sec.~\ref{sec:topol_codes}) are considered the most favourable codes in terms of their elegance, simplicity, high error-correction thresholds, and efficiency in resource overhead. Some such topological codes are particularly enticing, as they can be readily prepared from cluster states (Sec.~\ref{sec:CSQC}), which lend themselves naturally to certain networking methods, such as distributed state preparation.

>>>>

Importantly, topological codes do not require joint measurements across the entire graph state, instead requiring only operations localised to small regions within the graph. Thanks to this, computation using such topological codes can remain distributed\index{Distributed computation} without requiring the entire state to be held locally by a particular host, or requiring full access to the entire state by any particular user. As with cluster states, a large graph can be stitched together from a patchwork of smaller neighbouring graphs.

@@

Logical operations similarly have geometric interpretations. Most simply, logical Pauli-$\hat{X}$ and -$\hat{Z}$ gates may be implemented by applying chains of local Pauli operations along topological paths, specifically closed loops around the two different axes of the torus (Fig.~\ref{fig:toric_code_paulis}. These topologies may be deformed, provided that they are topologically equivalent to the desired closed loops, hence the name `topological code'. With more qubits and more elaborate gates, similar topological definitions exist for implementing logical gates on encoded qubits.

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{torus_paulis}
	\caption{Implementation of logical Pauli-$\hat{X}$ (\comment{which colour?}) and -$\hat{Z}$ (\comment{which colour?}) operations on a toric code qubit via the application of a chain of local Paulis. The chains must circumnavigate the torus around either axis. Any path topologically equivalent to such a circumnavigation of the torus is sufficient, enabling paths to bypass defects in the lattice.} \label{fig:toric_code_paulis}
\end{figure}

@@
